---
title: "COVID-19 multi estados"
date: "11/17/2020"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,message = FALSE)
mfit1=readRDS("Fit/fixed.rds")
mfit2=readRDS("Fit/random.rds")
mfit3=readRDS("Fit/random2.rds")
mfit4=readRDS("Fit/random2mod.rds")
library(bayesplot)
```

# Modelos

## Sin efectos aleatorios
Dimensión

$$
M_n \\
H_n \\
\mathbf{\eta}_n,\mathbf{\upsilon}_n \\
\mathbf{\theta}_m,\mathbf{\vartheta}_m \\
\mathbf{Q}^*_{nxm},\mathbf{Q}^{**}_{nxm} 
$$
Modelo

$$
\begin{aligned}
 {M}  &\sim Weibull(\alpha,\mathbf{\eta})\\
 {H}  &\sim Weibull(\alpha,\mathbf{\upsilon}) \\
 \mathbf{\eta} &= \exp(-\frac{\mu_m+\mathbf{Q}^*\mathbf{\vartheta}}{\alpha}) \\
 \mathbf{\upsilon} &= \exp(-\frac{\mu_h+\mathbf{Q}^{**}\mathbf{\theta}}{\alpha}) \\
 \alpha&=\exp(\alpha_r*10) \\
 \alpha_r&\sim N(0,1) \\
 \mu_m,\mu_h &\sim N(0,3) \\
 \mathbf{\vartheta},\mathbf{\theta} &\sim U(-\infty,\infty) \\
\end{aligned}
$$

$\mathbf{x}\mathbf{\beta}=\mathbf{Q}^*\mathbf{R}^*\mathbf{\beta}$ y $\mathbf{\vartheta}=\mathbf{R}^*\mathbf{\beta}$

## Un nivel

$$
\begin{aligned}
 M   &\sim Weibull(\alpha,\mathbf{\eta})\\
 H  &\sim Weibull(\alpha,\mathbf{\upsilon}) \\
 \mathbf{\eta} &= \exp(-\frac{\mu_m+\mathbf{\mu}_j^r+\mathbf{Q}^*\mathbf{\vartheta}}{\alpha}),\space\space j=1,...,32\\
 \mathbf{\upsilon} &= \exp(-\frac{\mu_h+\mathbf{Q}^{**}\mathbf{\theta}}{\alpha}) \\
 \mathbf{\mu}_j&=\sigma*\mathbf{\mu}_j^r \\
 \alpha&=\exp(\alpha^r*10) \\
 \alpha^r&\sim N(0,1) \\
 \mu^r_j&\sim N(0,1) \\
 \sigma&\sim t^+_3(0,1) \\
 \mu_m,\mu_h &\sim N(0,3) \\
 \mathbf{\vartheta},\mathbf{\theta} &\sim U(-\infty,\infty) \\
\end{aligned}
$$

$\sigma$ reparametrizada con gamma.

## Dos niveles

$$
\begin{aligned}
 M   &\sim Weibull(\alpha,\mathbf{\eta})\\
 H  &\sim Weibull(\alpha,\mathbf{\upsilon}) \\
 \mathbf{\eta} &= \exp(-\frac{\mu_m+\mathbf{\mu}_j^r+\mathbf{\mu}_k^r+\mathbf{Q}^*\mathbf{\vartheta}}{\alpha}),\space\space j=1,...,32,\space k=1,...,5\\
 \mathbf{\upsilon} &= \exp(-\frac{\mu_h+\mathbf{Q}^{**}\mathbf{\theta}}{\alpha}) \\
  \mathbf{\mu}_j&=\sigma_l*\mathbf{\mu}_j^r, \space\space l=1,2 \\
 \mathbf{\mu}_k&=\sigma_l*\mathbf{\mu}_k^r \\
 \alpha&=\exp(\alpha^r*10) \\
 \alpha^r&\sim N(0,1) \\
 \mu^r_j&\sim N(0,1) \\
 \sigma_l&\sim t^+_3(0,1) \\
 \mu_m,\mu_h &\sim N(0,3) \\
 \mathbf{\vartheta},\mathbf{\theta} &\sim U(-\infty,\infty) \\
\end{aligned}
$$

## Dos niveles contenidos

$k=1,...,138$

# Resultados

## Sin efectos aleatorios

```{r fig.align='center'}
mcmc_areas(
  mfit1,
  regex_pars = c("beta"),
  prob = 0.8,
  prob_outer = 0.95,
  point_est = "median"
)
```


```{r}
mfit1
```


## Un nivel

```{r}
mfit2
```

```{r fig.align='center',fig.height=20}
mcmc_intervals(
  mfit2,
  regex_pars = c("mu_l"),
  prob = 0.8,
  prob_outer = 0.95,
  point_est = "median"
)
```

## Dos niveles

```{r}
mfit3
```


```{r fig.align='center',fig.height=20}
mcmc_intervals(
  mfit3,
  regex_pars = c("mu_l"),
  prob = 0.8,
  prob_outer = 0.95,
  point_est = "median"
)
```


## Dos niveles contenidos

```{r}
mfit4
```

```{r fig.align='center',fig.height=40}
mcmc_intervals(
  mfit4,
  regex_pars = c("mu_l"),
  prob = 0.8,
  prob_outer = 0.95,
  point_est = "median"
)
```

# Por hacer

1. Artículo
2. Stan
- `loo` 
- $\tilde{y}$
3. Gráficas
- Parámetros
- Post Pred Checks
- Otros